Thermodynamic fragments in magic state theories

### 2021-02-16 magic_paper.tex
Replied to all comments, added scatter plot of Rate, made corrections to existing text. Next, I can try to plot the same scatter plot but for full majorization, or minus R_mana

Given this context, we can now state the following result, which is dependent on the free energy $F_\beta$ of a Gibbs state $\sigma$ where $ \beta F_\beta =  \beta\tr[H \sigma] - S(\sigma)$. We also fix the noisy Strange state to be of the form 
\begin{equation}
	\rho_{\rm{S}}(\epsilon) \coloneqq (1-\epsilon)\ketbra{\rm{S}} + \epsilon \frac{1}{3}\id,
\end{equation}
but more general states can be handled in exactly the same manner.
\begin{theorem}Let $\sigma$ be a qutrit stabilizer state, given by $\sigma = \frac{1}{\Z} e^{-\beta H}$ with $H$ having eigenvalues $E_0 \le E_1 \le E_2$, and where $\beta$ is an (effective) inverse temperature for the state. Then any distillation rate $R$ in the $\sigma$-fragment is bounded as follows.
If \ddd{[Conditions]}
\begin{equation}
	R \leq 1 + \frac{\ln{\left( 1 - \frac{4}{3}\epsilon \right)}}{\beta (E_0 - F_\beta)},
\end{equation}
Or if \ddd{[I need to insert conditions]}
\begin{equation}
	R \le 1 + \frac{\ln{\left(1-\frac{1}{3}\epsilon \right)} + (E_2 - E_0)(\beta_{\star} - \beta)}{\beta (E_0 - F_\beta)},
\end{equation}
Or finally if \ddd{[I need to insert conditions]}
\begin{equation}
	R \leq  1+ \frac{\ln{\left(1-\frac{1}{3}\epsilon \right)}}{-\ln{2} + \beta (E_2 - F_\beta)},
\end{equation}
where
\begin{equation}
	\epsilon_{\star}(\beta) := 3 - \dfrac{18}{8-e^{(E_2 - E_0)\beta}}.
\end{equation}
is a threshold error rate.
\end{theorem}

@@

\ddd{Note the following is relevant: you might have $W_{\bmq} = W_{\bmq'}$ for two different $\bmq$, $\bmq'$. This would make a difference to our calculations for the first elbow. Check this doesn't occur. (If it does, our analysis is still correct, but it simply could be improved).}
\nick{This is in general true, will check if in our case it makes a difference}

@@

There are four distinct values of the Gibbs-rescaled distribution on the phase space, with the negative Strange component $-v$ corresponding to energy $E_0$ as illustrated in the phase space split in~\cref{fig:pd_split_thermal}.
The Wigner-component vectors $\bmw(\rho_{\rm{S}}), \bmw(\gamma)$ are then constructed so as to match the four phase space regions.
\begin{figure}[h]
    \centering
    \includegraphics[scale=0.5]{figs/pd_split_thermal.pdf}
    \caption{\textbf{Qutrit phase space regions with different Gibbs-rescaled values.}
    The slope is negative in region $1$ and positive in regions $X,Y,Z$.
    It attains a unique value in each region, given by~\cref{eq:bmw_rescaled} respectively.
    }
    \label{fig:pd_split_thermal}
\end{figure}

@@

Given an even value $\alpha$ for the sum, the term $v^{n-\alpha} u^{\alpha} e^{-\beta (n-\alpha)E_0}$ is fixed, so the expression is maximised by setting the coefficient of the highest energy $E_{\rm{max}}$ equal to $\alpha$.
Hence, we have
\begin{align}
	&\bmw(\rho_{\rm{S}} | \gamma)_{\rm{max}} = \nonumber\\
	&(3\Z)^{n} \max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ v^{n-\alpha} u^{\alpha} e^{\beta (n-\alpha)E_0} e^{\beta \alpha E_{\rm{max}}} \Big\}} =  \nonumber\\
	&(3\Z)^{n} v^n e^{n\beta E_0}\max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ \left( \frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)} \right)^{\alpha} \Big\}}
\end{align}
If the expression $\frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)}$ is less than $1$ then the maximum occurs at $\alpha=0$, and otherwise the maximum occurs at $\alpha = n$. To determine this transition we set
\begin{equation}
\frac{u(\epsilon)}{v(\epsilon)} e^{\beta (E_{\rm{max}} - E_0)} =1,
\end{equation}
and solve for $\epsilon$ as a function of $\beta$. We denote the value value of $\epsilon$ for which this occurs $\epsilon_{\star}$ and find that it is equal to
\begin{equation}
	\epsilon_{\star}(\beta) := 3 - \dfrac{18}{8-e^{(E_{\rm{max}} - E_0)\beta}}.
\end{equation}
For the case $E_{\rm{max}} = E_0$, namely the negative component overlaps the highest energy state distribution, this threshold is constant in temperature and given by $\epsilon_{\star} = 3/7$.

Otherwise, we have that the negative component does not overlap with the highest energy state and so $ E_{\rm max} - E_0 > 0$. For this regime the threshold $\epsilon_{\star} (\beta)$ is a decreasing function of $\beta$, and it achieves its maximum value $3/7$ for $\beta = 0$, namely on the unital fragment. It also attains a value $0$ for
\begin{equation}
	\beta_{\star} \coloneqq \frac{1}{E_{\rm{max}} - E_0} \ln2.
\end{equation}
For $\beta > \beta_{\star}$, $\epsilon_{\star}$ is negative, meaning that the noise level $\epsilon$ will always be higher than the threshold. \ddd{For $\beta \rightarrow \infty$ surely $\epsilon_{\star} \rightarrow 3$, and so it goes negative, but then goes positive again? I.e. there's another temperature region to consider. What am I missing here?}

We note that the threshold becomes $0$ when the difference between the maximum energy level and the level associated with the state negativity is equal to the energy extracted from a single particle Szilard's engine,
\begin{equation}
	E_{\rm{max}} - E_0 = kT_{\star} \ln2.
\end{equation}

The maximum value of the Gibbs-rescaled distribution finally is
\begin{equation}
\bmw(\rho_{\rm{S}} | \gamma)_{\rm{max}} =
	\begin{cases}
		(3\Z)^{n} v^n e^{n\beta E_0}, &\epsilon \leq \epsilon_{\star},\ \hspace{30pt}\rm{(C1)}	\\
		(3\Z)^{n} u^n e^{n\beta E_{\rm{max}}}, &\epsilon > \epsilon_{\star}.\ \hspace{32pt}\rm{(C2)} 
	\end{cases}
\end{equation}
Case $\rm{(C1)}$ corresponds to $(i,j,k) = (0,0,0)$, while case $\rm{(C2)}$ corresponds to the  the conditions 
\begin{equation}
	(i,j,k) = 
	\begin{cases}
	(0,n,0), &\text{if } E_{\rm{max}} = E_1, \\
	(0,0,n), &\text{if } E_{\rm{max}} = E_2.
	\end{cases}
\end{equation}
Note that if $E_{\rm{max}} = E_0$, we get $\epsilon_{\star} = 3/7$ and $\rm{(C1)}$ holds for all $\epsilon$ and $\beta$.
Assuming $E_{\rm{max}} > E_0$, we get the cases:
\begin{itemize}
	\item $\beta = 0$. Then, $\epsilon_{\star} = 3/7$ and $\rm{(C1)}$ holds for all noise levels $\epsilon$.
	This is the unital fragment.
	\item $0 < \beta < \beta_{\star}$. Then, $0 < \epsilon_{\star} < 3/7$ and $\rm{(C1)}$ holds for $\epsilon \leq \epsilon_{\star}$, while $\rm{(C2)}$ holds for $\epsilon \geq \epsilon_{\star}$.
	\item $\beta \geq \beta_{\star}$. Then, $ \epsilon_{\star} \leq 0$ and $\rm{(C2)}$ holds for all $\epsilon$.
\end{itemize}

@@

The Lorenz curves of the initial and target states may each be described by either $\rm{(C1)}$ or $\rm{(C2)}$, depending on the physical parameters $\epsilon, \epsilon', \beta$.
Specifically, we can get three scenarios:
\begin{enumerate}
	\item $\rm{(C1)} \rightarrow \rm{(C1)}$ if $E_{\rm{max}} = E_0$ OR $E_{\rm{max}} > E_0$, $\beta < \beta_{\star}$ and $\epsilon' < \epsilon  \leq \epsilon_{\star}$.
	\item $\rm{(C2)} \rightarrow \rm{(C1)}$ if $E_{\rm{max}} > E_0$, $\beta < \beta_{\star}$ and $\epsilon' \leq \epsilon_{\star} < \epsilon$.
	\item $\rm{(C2)} \rightarrow \rm{(C2)}$ if $E_{\rm{max}} > E_0$, $\beta \geq \beta_{\star}$.
\end{enumerate}
Note that $\rm{(C1)} \rightarrow \rm{(C2)}$ is impossible because it would imply $\epsilon \leq \epsilon_{\star} \leq \epsilon' < \epsilon$, a contradiction.

@@

We now compute distillation bounds based on the first elbow constraint in the three possible scenarios. \ddd{[Does anything special happen if we have degeneracies in energy? ]}
We express them in terms of the free energy of thermal state $\gamma_\beta$ denoted by
\begin{equation}
	F_\beta \coloneqq \tr[\gamma_\beta H] + \beta^{-1} \tr[\gamma_\beta \ln{\gamma_\beta}] = -\beta^{-1} \ln{\Z_\beta}.
\end{equation}
Substituting coordinates from~\cref{eq:first_elb_coords} appropriately in~\cref{eq:first_elb_bound}, we get the following necessary conditions:
\begin{enumerate}
	\item $\rm{(C1)} \rightarrow \rm{(C1)}$ if $E_{\rm{max}} = E_0$ OR $E_{\rm{max}} > E_0$, $\beta < \beta_{\star}$ and $\epsilon' < \epsilon  \leq \epsilon_{\star}$.

\begin{align}
	\frac{n}{n'} &\geq \frac{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E_0 - F_\beta)}{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (E_0 - F_\beta)}, \text{ or} \\
	\epsilon &\leq \frac{3}{4} - \frac{3}{4} \left( 1 - \frac{4}{3}\epsilon' \right)^{\frac{n'}{n}} \left( \frac{e^{-\beta E_0}}{\Z_\beta} \right)^{1 - \frac{n'}{n}}	
\end{align}
This leads to an upper bound for the distillation rate $R=n'/n$ of pure Strange states ($\epsilon' = 0$),
\begin{equation}
	R \leq R(\beta) \coloneqq 1 - \frac{\ln{\left( \frac{1}{1 - \frac{4}{3}\epsilon} \right)}}{\beta (E_0 - F_\beta)},
\end{equation}

@@

@@

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.5]{figs/distill_bounds_temp.pdf}
    \caption{\textbf{Distillation rate with low noise in thermal fragments.} Distillation rates obtained by majorization $R(\beta)$ for low noise levels $\epsilon \leq \epsilon_{\star}$ are plotted for different temperatures $\beta^{-1}$ such that $0 \leq \beta \leq \beta_{\star}$.
    The mana distillation rate $R_{\rm{mana}}$ is given for comparison.
    The Hamiltonian spectrum is simple harmonic, $(E_0, E_1, E_2) = (0,1,2)$.
    As $\beta$ increases, the range of noise levels for which $R(\beta)$ is valid decreases and the distillation bound becomes stricter.
\nick{it holds for $0 \leq \epsilon \leq \epsilon_*$, where $\epsilon_\star$ is the noise level ($ \leq \epsilon_{\star}$) at which the state conversion turns from $\rm{(C1)} \rightarrow \rm{(C1)}$ to $\rm{(C2)} \rightarrow \rm{(C1)}$. Need to adjust~\cref{fig:distill_bounds_temp} accordingly}
    }
    \label{fig:distill_bounds_temp}
\end{figure}

>>>>

Given this context, we can now state the following result, which is dependent on the free energy $F_\beta$ of a Gibbs state $\sigma$ where $ \beta F_\beta =  \beta\tr[H \sigma] - S(\sigma)$. We also fix the noisy Strange state to be of the form 
\begin{equation}
	\rho_{\rm{S}}(\epsilon) \coloneqq (1-\epsilon)\ketbra{\rm{S}} + \epsilon \frac{1}{3}\id,
\end{equation}
but more general states can be handled in exactly the same manner.
\begin{theorem}Let $\sigma$ be a qutrit stabilizer state, given by $\sigma = \frac{1}{\Z} e^{-\beta H}$ with $H$ having eigenvalues $E_0 \le E_1 \le E_2$, and where $\beta$ is an (effective) inverse temperature for the state. Then any distillation rate $R$ in the $\sigma$-fragment is bounded as follows.
If $\beta \leq \beta_{\star}$ and $\epsilon' < \epsilon  \leq \epsilon_{\star}$,
\begin{equation}
	R \leq 1 + \frac{\ln{\left( 1 - \frac{4}{3}\epsilon \right)}}{\beta (E_0 - F_\beta)},
\end{equation}
Or if $\beta \leq \beta_{\star}$ and $\epsilon' \leq \epsilon_{\star} < \epsilon$
\begin{equation}
	R \le 1 + \frac{\ln{\left(1-\frac{1}{3}\epsilon \right)} - (E_2 - E_0)(\beta_{\star} - \beta)}{\beta (E_0 - F_\beta)},
\end{equation}
Or finally if $\beta > \beta_{\star}$
\begin{equation}
	R \leq  1+ \frac{\ln{\left(1-\frac{1}{3}\epsilon \right)}}{-\ln{2} + \beta (E_2 - F_\beta)},
\end{equation}
where
\begin{equation}
	\beta_\star \coloneqq \frac{1}{E_2 - E_0} \ln{2}
\end{equation}
is a threshold temperature and for $\beta \leq \beta_\star$,
\begin{equation}
	\epsilon_{\star}(\beta) \coloneqq 3 - \dfrac{18}{8-e^{(E_2 - E_0)\beta}}.
\end{equation}
is a threshold error rate.
\end{theorem}

@@

\ddd{Note the following is relevant: you might have $W_{\bmq} = W_{\bmq'}$ for two different $\bmq$, $\bmq'$. This would make a difference to our calculations for the first elbow. Check this doesn't occur. (If it does, our analysis is still correct, but it simply could be improved).}
\nick{It can occur accidentally, but it doesn't make a difference for first elbow analysis, as we ``bring the top Lorenz curve down till its first elbow touches the bottom Lorenz curve''. Basically, Lorenz curves have fewer elbows, but because the first elbow constraint boils down to a ratio comparison~\cref{eq:first_elb_bound} it doesn't change the analysis.}

@@

There are four distinct values of the Gibbs-rescaled distribution on the phase space, with the negative Strange component $-v$ corresponding to energy $E_0$ as illustrated in the phase space split in~\cref{fig:pd_split_thermal}.
The Wigner-component vectors $\bmw(\rho_{\rm{S}}), \bmw(\gamma)$ are then constructed so as to match the four phase space regions.
\begin{figure}[h]
    \centering
    \includegraphics[scale=0.5]{figs/pd_split_thermal.pdf}
    \caption{\textbf{Qutrit phase space regions with different Gibbs-rescaled values.}
    The Gibbs-rescaled distribution attains a unique value in each region $1,X,Y,Z$, given by~\cref{eq:bmw_rescaled} respectively.
    }
    \label{fig:pd_split_thermal}
\end{figure}

@@

Given an even value $\alpha$ for the sum, the term $v^{n-\alpha} u^{\alpha} e^{-\beta (n-\alpha)E_0}$ is fixed, so the expression is maximised by setting the coefficient of the highest energy $E_{\rm{max}}$ equal to $\alpha$.
Hence, we have
\begin{align}
	&\bmw(\rho_{\rm{S}} | \gamma)_{\rm{max}} = \nonumber\\
	&(3\Z)^{n} \max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ v^{n-\alpha} u^{\alpha} e^{\beta (n-\alpha)E_0} e^{\beta \alpha E_{\rm{max}}} \Big\}} =  \nonumber\\
	&(3\Z)^{n} v^n e^{n\beta E_0}\max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ \left( \frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)} \right)^{\alpha} \Big\}}
\end{align}
If the expression $\frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)}$ is less than $1$ then the maximum occurs at $\alpha=0$, and otherwise the maximum occurs at $\alpha = n$. To determine this transition we set
\begin{equation}
	\frac{u(\epsilon)}{v(\epsilon)} e^{\beta (E_{\rm{max}} - E_0)} = 1.
\end{equation}
This can be rewritten as
\begin{equation}\label{eq:noise_transition}
	\frac{3-\epsilon}{6-8\epsilon} e^{\beta (E_{\rm{max}} - E_0)} = 1.
\end{equation}
The function $(3-\epsilon) / (6-8\epsilon)$ is increasing in $\epsilon$, achieving its minimum value $1/2$ at $\epsilon = 0$ and its maximum value $1$ at $\epsilon = 3/7$.
We want to find in which cases there exists a threshold noise level $\epsilon_\star$ at which the transition in~\cref{eq:noise_transition} occurs.

For the case $E_{\rm{max}} = E_0$, namely when the negative component overlaps the highest energy state distribution, this threshold is constant in temperature and given by $\epsilon_{\star} = 3/7$.

There is a threshold temperature value $\beta_\star$ given by
\begin{equation}
	\beta_{\star} \coloneqq \frac{1}{E_{\rm{max}} - E_0} \ln2.
\end{equation}
Below the threshold temperature, $0 \leq \beta \leq \beta_\star$, the transition is well defined and the threshold noise level at which it occurs is given by
\begin{equation}
	\epsilon_{\star}(\beta) := 3 - \dfrac{18}{8-e^{(E_{\rm{max}} - E_0)\beta}}.
\end{equation}
This encompasses the case $E_{\rm{max}} = E_0$.

We note that the threshold noise level $\epsilon_\star$ becomes $0$ when $\beta = \beta_\star$, namely the difference between the maximum energy level and the level associated with the state negativity is equal to the energy extracted from a single particle Szilard's engine,
\begin{equation}
	E_{\rm{max}} - E_0 = kT_{\star} \ln2.
\end{equation}

For $\beta > \beta_\star$, we have
\begin{equation*}
	\frac{3-\epsilon}{6-8\epsilon} e^{\beta (E_{\rm{max}} - E_0)} > \frac{3-\epsilon}{6-8\epsilon} 2 \geq \frac{1}{2}2 = 1,
\end{equation*}
so there is no transition and the threshold noise level remains $\epsilon_\star = 0$.

The maximum value of the Gibbs-rescaled distribution finally is
\begin{equation}
\bmw(\rho_{\rm{S}} | \gamma)_{\rm{max}} =
	\begin{cases}
		(3\Z)^{n} v^n e^{n\beta E_0}, &\epsilon \leq \epsilon_{\star},\ \hspace{30pt}\rm{(C1)}	\\
		(3\Z)^{n} u^n e^{n\beta E_{\rm{max}}}, &\epsilon > \epsilon_{\star}.\ \hspace{32pt}\rm{(C2)} 
	\end{cases}
\end{equation}
Case $\rm{(C1)}$ corresponds to $(i,j,k) = (0,0,0)$, while case $\rm{(C2)}$ corresponds to the  the conditions 
\begin{equation}
	(i,j,k) = 
	\begin{cases}
	(0,n,0), &\text{if } E_{\rm{max}} = E_1, \\
	(0,0,n), &\text{if } E_{\rm{max}} = E_2.
	\end{cases}
\end{equation}
Note that if $E_{\rm{max}} = E_0$, we get $\epsilon_{\star} = 3/7$ and $\rm{(C1)}$ holds for all $\epsilon$ and $\beta$.
Assuming $E_{\rm{max}} > E_0$, we get the cases:
\begin{itemize}
	\item $\beta = 0$. Then, $\epsilon_{\star} = 3/7$ and $\rm{(C1)}$ holds for all noise levels $\epsilon$.
	This is the unital fragment.
	\item $0 < \beta \leq \beta_{\star}$. Then, $0 \leq \epsilon_{\star} < 3/7$ and $\rm{(C1)}$ holds for $\epsilon \leq \epsilon_{\star}$, while $\rm{(C2)}$ holds for $\epsilon \geq \epsilon_{\star}$.
	\item $\beta > \beta_{\star}$. Then, $ \epsilon_{\star} = 0$ and $\rm{(C2)}$ holds for all $\epsilon$.
\end{itemize}

@@

The Lorenz curves of the initial and target states may each be described by either $\rm{(C1)}$ or $\rm{(C2)}$, depending on the physical parameters $\epsilon, \epsilon', \beta$.
Specifically, we can get three scenarios:
\begin{enumerate}
	\item $\rm{(C1)} \rightarrow \rm{(C1)}$ if $E_{\rm{max}} = E_0$ OR $E_{\rm{max}} > E_0$, $\beta < \beta_{\star}$ and $\epsilon' < \epsilon  \leq \epsilon_{\star}$.
	\item $\rm{(C2)} \rightarrow \rm{(C1)}$ if $E_{\rm{max}} > E_0$, $\beta < \beta_{\star}$ and $\epsilon' \leq \epsilon_{\star} < \epsilon$.
	\item $\rm{(C2)} \rightarrow \rm{(C2)}$ if $E_{\rm{max}} > E_0$, $\beta \geq \beta_{\star}$.
\end{enumerate}
Note that $\rm{(C1)} \rightarrow \rm{(C2)}$ is impossible because it would imply $\beta < \beta_{\star}$ and $\epsilon \leq \epsilon_{\star} \leq \epsilon' < \epsilon$, a contradiction.

@@

We now compute distillation bounds based on the first elbow constraint in the three possible scenarios. \ddd{[Does anything special happen if we have degeneracies in energy? ]}
\nick{If we have degeneracies, basically the Gibbs-rescaled distribution in~\cref{eq:bmw_rescaled} has some equal components, so Lorenz curves have fewer elbows, but because the first elbow constraint boils down to a ratio comparison~\cref{eq:first_elb_bound} it doesn't change the analysis}
We express them in terms of the free energy of thermal state $\gamma_\beta$ denoted by
\begin{equation}
	F_\beta \coloneqq \tr[\gamma_\beta H] + \beta^{-1} \tr[\gamma_\beta \ln{\gamma_\beta}] = -\beta^{-1} \ln{\Z_\beta}.
\end{equation}
Substituting coordinates from~\cref{eq:first_elb_coords} appropriately in~\cref{eq:first_elb_bound}, we get the following necessary conditions:
\begin{enumerate}
	\item $\rm{(C1)} \rightarrow \rm{(C1)}$ if $E_{\rm{max}} = E_0$ OR $E_{\rm{max}} > E_0$, $\beta < \beta_{\star}$ and $\epsilon' < \epsilon  \leq \epsilon_{\star}$.

\begin{align}
	\frac{n}{n'} &\geq \frac{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E_0 - F_\beta)}{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (E_0 - F_\beta)}, \text{ or} \\
	\epsilon &\leq \frac{3}{4} - \frac{3}{4} \left( 1 - \frac{4}{3}\epsilon' \right)^{\frac{n'}{n}} \left( \frac{e^{-\beta E_0}}{\Z_\beta} \right)^{1 - \frac{n'}{n}}	
\end{align}
This leads to an upper bound for the distillation rate $R=n'/n$ of pure Strange states ($\epsilon' = 0$),
\begin{equation}
	R \leq R(\epsilon, \beta) \coloneqq 1 - \frac{\ln{\left( \frac{1}{1 - \frac{4}{3}\epsilon} \right)}}{\beta (E_0 - F_\beta)},
\end{equation}

@@

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.5]{figs/noise_threshold.pdf}
    \caption{\textbf{Noise threshold $\epsilon_\star$ and rate $R(\beta, \epsilon_\star)$ versus $\beta$.}
    At $\beta = 0$ and threshold noise level $\epsilon = \epsilon_\star = 3/7$, the rate is $R(0, \epsilon_\star) = \frac{\ln{(9/7)}}{\ln{3}} \approx 0.23$.
    }
    \label{fig:noise_threshold}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.5]{figs/rate_contour.png}
    \caption{\textbf{Rate $R(\beta, \epsilon)$ versus $\beta$ and $\epsilon$.}
    The vertical dashed line indicates the temperature threshold $\beta_\star$ and the diagonal dashed curve indicates the noise threshold $\epsilon_\star$ at every $\beta \leq \beta_\star$.
    }
    \label{fig:rate_contour}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.5]{figs/distill_bounds_temp.pdf}
    \caption{\textbf{Distillation rate with low noise in thermal fragments.} Distillation rates obtained by majorization $R(\beta)$ for low noise levels $\epsilon \leq \epsilon_{\star}$ are plotted for different temperatures $\beta^{-1}$ such that $0 \leq \beta \leq \beta_{\star}$.
    The mana distillation rate $R_{\rm{mana}}$ is given for comparison.
    The Hamiltonian spectrum is simple harmonic, $(E_0, E_1, E_2) = (0,1,2)$.
    As $\beta$ increases, the range of noise levels for which $R(\beta)$ is valid decreases and the distillation bound becomes stricter.
    }
    \label{fig:distill_bounds_temp}
\end{figure}
